Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-07 ms.tex
I removed an extra s after a figure caption.
I added some example runs with a Log-Normal particle size distribution.

I did an initial MCMC fit where I plugged in these same index of refraction (n=1.825 - 0.001 $i$ for all wavelengths) and fit the spectrum that I found in IDL.
The best fit matches the data well with a $\bar{\chi^2}$ of 1.3, visible in Figure \ref{fig:mcmcMieBest1particle}.
However, there are many solutions at different resonances in the Mie extinction curve visible in Figure \ref{fig:mcmcMieCorner1particle}.
A better way to handle this is a log-normal distribution of particles as in \citet{schlawin2016}.

\begin{figure*}[!t]
\centering
\subfloat[Single Particle Best fit for \shb]{
	\includegraphics[width=0.5\textwidth]{best_fit_single_particle_mie.pdf}
	\label{fig:mcmcMieBest1particle}
	}
\subfloat[Single Particle Histograms for \shb]{
	\includegraphics[width=0.5\textwidth]{corner_single_particle_mie.pdf}
	\label{fig:mcmcMieCorner1particle}
	}
	\caption{An initial fit to the amplitude spectrum when using a single particle.
	The best fit nicely matches the data but has multiple solutions at the Mie scattering resonances.}
	\label{fig:mcmcMieCorner1particle}s
	\vspace{0.1in}
\end{figure*}

>>>>

I did an initial MCMC fit where I plugged in these same index of refraction (n=1.825 - 0.001 $i$ for all wavelengths) and fit the spectrum that I found in IDL.
The best fit matches the data well with a $\bar{\chi^2}$ of 1.3, visible in Figure \ref{fig:mcmcMieBest1particle}.
However, there are many solutions at different resonances in the Mie extinction curve visible in Figure \ref{fig:mcmcMieCorner1particle}.
A better way to handle this is a log-normal distribution of particles as in \citet{2016ApJ...826..156S}.

\begin{figure*}[!t]
\centering
\subfloat[Single Particle Best fit for \shb]{
	\includegraphics[width=0.5\textwidth]{best_fit_single_particle_mie.pdf}
	\label{fig:mcmcMieBest1particle}
	}
\subfloat[Single Particle Posterios for \shb]{
	\includegraphics[width=0.5\textwidth]{corner_single_particle_mie.pdf}
	\label{fig:mcmcMieCorner1particle}
	}
	\caption{An initial fit to the amplitude spectrum when using a single particle.
	The best fit nicely matches the data but has multiple solutions at the Mie scattering resonances.}
	\label{fig:mcmcMieCorner1particle}
	\vspace{0.1in}
\end{figure*}

I manually created a log-normal distribution of particles in Python and added up their cross sections weighted by number of particles.
This process is slow, so I calculated it once and found  a 15th order polynomial fit to $Q_{ext}$ and evaluated this in the model.
The resulting MCMC distribution is shown in Figure \ref{fig:mcmcMieCornerLogNorm}.

\begin{figure*}[!t]
\centering
\subfloat[Log-Normal Best fit for \shb]{
	\includegraphics[width=0.5\textwidth]{best_fit_lognormal_mie.pdf}
	\label{fig:mcmcMieBestLogNorm}
	}
\subfloat[Log-Normal Posteriors for \shb]{
	\includegraphics[width=0.5\textwidth]{corner_lognormal_mie.pdf}
	\label{fig:mcmcMieCornerLogNorm}
	}
	\caption{An initial fit to the amplitude spectrum when using a log-normal size distribution with a $\sigma=0.5$.
	Again, there are a few ``walkers'' that stay at large radii.}
	\label{fig:mcmcMieCornerLogNorm}
	\vspace{0.1in}
\end{figure*}
